Hector Permafrost

### 2019-01-10 analysis/paper/paper.Rmd
PAPER: Add more notes and references

@@

>>>>

(Previous work on modeling permafrost)
[@burke_2017_quantifying] -- JULES and ORCHIDEE, with new permafrost scheme, combined with intermediate complexity climate-ocean model (IMOGEN), to look at climate sensitivity to permafrost C emissions.

@@

Temperature amplification of permafrost carbon feedback (by 2100) 0.02 to 0.36 °C [@burke_2013_estimating; @schneider_2012_estimating; @schneider_2015_observation], or 0.1 to 0.8 °C in [@macdougall_2012_significant; @macdougall_2013_if], or 10-40% of peak temperature change [@crichton_2016_permafrost], or 0.2 to 12% [@burke_2017_quantifying].

Permafrost carbon has greater impact at lower emissions scenarios [@burke_2017_quantifying; @macdougall_2012_significant; @macdougall_2013_if] .
